% Effects of telluric lines, as demonstrated via simulation

\documentclass{emulateapj}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
\citestyle{aa}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

% chinese character for name
\usepackage{CJK}

\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\bcm{\begin{comment}}
\def\ecm{\end{comment}}
\def\mps{m~s$^{-1}$}
\def\msini{M\sin{i}}
\def\mjup{M_{\rm Jup}}
\def\msol{M_{\odot}}

\slugcomment{}
\shorttitle{}
\shortauthors{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{CJK*}{UTF8}{gbsn}

\title
{
The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine
Cell as Calibrators\altaffilmark{1}
}

\altaffiltext{1}
{
Based on observations observations obtained at the Keck Observatory, which is operated
by the University of California.  The Keck Observatory was made
possible by the generous financial support of the W. M. Keck
Foundation.
}

\author{Sharon Xuesong Wang (王雪凇)\altaffilmark{2,3},
  Jason T. Wright\altaffilmark{2,3}} % primary work force
\author{Chad Bender\altaffilmark{2,3}} % lots of help with TERRASPEC
                                % and consultation on telluric lines
\author{Andrew W. Howard\altaffilmark{4}} % Keck
\author{Geoffrey W. Marcy\altaffilmark{5}} % Keck
\author{Howard Isaacson\altaffilmark{5}} % Keck
\author{Suvrath Mahadevan\altaffilmark{2,3}} % comments and suggestions


\altaffiltext{2}{Department of Astronomy and Astrophysics, 525 Davey
  Laboratory, The Pennsylvania State University, University Park, PA
  16802, USA; Send correspondence to xxw131@psu.edu and
  jtwright@astro.psu.edu}

\altaffiltext{3}{Center for Exoplanets and Habitable Worlds, 525 Davey
  Laboratory, The Pennsylvania State University, University Park, PA
  16802, USA}

\altaffiltext{4}{Hawaii, USA}

\altaffiltext{5}{Department of Astronomy, University of California,
  Berkeley, CA 94720, USA}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Tellurics are bad and you really don't want them. Here's how to get
rid of them.

\end{abstract}

\keywords{instrumentation}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

We are going to cite \cite{artigau2014, cunha2014} and
\cite{hitran2013}.

Jason's suggestions:

- run tau Ceti as target #2

- don't show our classic before+after+difference RV vs. BC, just show
the difference, especially the talk

- show actual data for sig Dra RV vs. BC of Keck, to show that this is
real, it should be standard to plot RV vs. BC to check systematics
(i.e. tellurics)

- Mention Vogt APF paper sig Dra planet.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}\label{sec:method}

Introduction to Keck/HIRES CPS data,


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Keck/HIRES Spectra}

ZZZ Plots:

- comparison between simulated and observed Keck/HIRES spectra: blaze,
and zoom in.

- comparison between SME stellar template and empirical, deconvolved
template.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Injection of Telluric Lines}

Description of TERRASPEC.

ZZZ Plots:

- telluric line atlas in the optical? just to demonstrate where they are.

- simulated observation and template with injected tellurics,
overplotted with clean simulated spectra, which would also demonstrate
that due to BC, lines will pull on each other.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction of Radial Velocities}

Introduction to Doppler code and relevant adoption part for the
simulation.

How the end product RVs are computed (vanking, or other weighting schemes).


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of Telluric Lines on RV Precision}

ZZZ Plots:

- telluric free simulations to demonstrate RV precision, vs. year,
vs. BC

- telluric injected simulations to demonstrate effects, vs. year, vs. BC

- RV vs. BC for chunks with and without telluric lines before and
after injection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Remedies and Their Effectiveness}

ZZZ Plots:

- demonstration of effectiveness and ineffectiveness of double masking.

- demonstration of effectiveness of a clean template and forward
modeling tellurics.

- demonstration of precision required for modeling tellurics, and
maximum tolerance for template `cleaness'. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Future Work}\label{sec:summary}

Work on actual observations!


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Then Acknowledgement
% Thank John Johnson for providing CPS Doppler code.
\acknowledgements
% John
The authors thank John A. Johnson for providing a copy of his Doppler
code and his help with our incorporation of the code into the HET
pipeline.  The authors also thank Debra Fischer for her assistance in
this regard.

% CEHW
This work was partially supported by funding from the Center for
Exoplanets and Habitable Worlds, which is supported by the
Pennsylvania State University, the Eberly College of Science, and the
Pennsylvania Space Grant Consortium.

% Financial support acknowledgement
The authors appreciate the significant Keck observing time and
associated funding support from NASA for the study of long period
planets and mulitplanet systems.
%
J.T.W.\ and S.X.W.\ acknowledge support from NASA Origins of Solar
Systems grant NNX10AI52G.

% Keck
The work herein is based on observations obtained at the W. M. Keck
Observatory, which is operated jointly by the University of California
and the California Institute of Technology.  The Keck Observatory was
made possible by the generous financial support of the W.M. Keck
Foundation.  We wish to recognize and acknowledge the very significant
cultural role and reverence that the summit of Mauna Kea has always
had within the indigenous Hawaiian community.  We are most fortunate
to have the opportunity to conduct observations from this mountain.

% HET
The Hobby-Eberly Telescope is a joint project of the University of
Texas at Austin, the Pennsylvania State University, Stanford
University, Ludwig Maximillians Universit\"at M\"unchen, and Georg
August Universit\"at G\"ottingen. The HET is named in honor of its
principal benefactors, William P. Hobby and Robert E. Eberly.

% ADS
This work has made use NASA’s Astrophysics Data System Bibliographic Services.


\end{CJK*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Bibliography
%\bibliographystyle{apj} % (uses file "xxx.bst")
%\bibliography{mn-jour,references}%,bootstrap-ref}
\bibliography{references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}
